\documentclass[10pt,letterpaper]{letter}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\address{
Christopher C. Lamb \\
7400 Yarwood St. NE \\
Albuquerque, NM 87109
} 
\signature{Christopher C. Lamb, Ph.D, CISSP} 
\begin{document} 
\begin{letter}{
%Mandiant \\
%2318 Mill Road Ste. 500 \\
%Alexandria, VA 22314
} 
\opening{To most fabulous Mandiant employee:} 
 
I am thrilled to have an opportunity to apply for a position with Mandiant.  Quite a few of my colleagues from Sandia National Laboratories (SNL) have found challenging and interesting work with you, and I have heard nothing but good things about the company itself and those working within it.

I am currently a Principal Computer Scientist working on research and development at SNL.  Recently, I have worked with both internal and external customers in such areas as malware countermeasure design, large scale architectures for malware analytics, and cyber-physical sensor event analysis and knowledge extraction. In the first two projects, work was focused on designing systems able to detect anomalous network traffic in previously established large-scale perimeter-centric solutions.  The third project is focused on developing algorithms and components capable of analyzing both streaming and captured data for both known and unknown information.  In other work, over the past few years, I have developed both large-scale distributed systems and embedded systems supporting specific missions for internal and external clients.

I also currently hold an appointment as research faculty in the Electrical and Computer Engineering Department at the University of New Mexico (UNM).  While there, I have been engaged in research addressing how to apply security primitives dynamically to cloud-computing systems, usage management design and implementation, software-defined infrastructural control and provisioning, and cloud robotics.

From a specific technical perspective, I have used a wide variety of programming languages and frameworks in the course of my work, ranging from C to Java to Python to R. I currently use both OpenStack and Hadoop in my research. 

With my background and experience, I feel I would be an excellent fit for the large scale data analysis research position currently open in the Albuquerque, New Mexico area.  I very much look forward to discussing this with you further.
 
\closing{Sincerely,} 
%\cc{Cclist} 
%\ps{adding a postscript} 
%\encl{list of enclosed material} 
\end{letter} 
\end{document}