\documentclass[margin,line]{resume}

\begin{document}
\name{\Large Christopher C. Lamb}
\begin{resume}

\section{\mysidestyle Contact\\Information}
Sandia National Laboratories					\hfill office: 505.284.2379				\vspace{0mm}\\\vspace{0mm}%
Science and Engineering Information Systems	\hfill mobile: 505.228.8090      		\vspace{0mm}\\\vspace{0mm}%
Albuquerque, NM 87109						\hfill e-mail: cclamb@sandia.gov		  	\vspace{0mm}\\\vspace{-4.5mm}%

\section{\mysidestyle Education}

\textbf{Ph.D Computer Engineering} \\
\textsl{University of New Mexico} \hfill \textbf{ January 2007 -- present}
\begin{list2}\vspace{2mm}
\item Expected graduation date: December 2012
\item Advisor:  Professor Greg Heileman
\item Dissertation Topic: Information Protection in Content-centric Networks
\end{list2}%\vspace{-1.5mm}
{\bf M.S. Computer Science}, University of New Mexico \\ %\textit{M.S. Computer Science, University of New Mexico} \\
{\bf B.S. Mechanical Engineering}, New Mexico State University %\textit{B.S. Mechanical Engineering, New Mexico State University}

\section{\mysidestyle Certifications}
TOGAF 9 Certified Enterprise Architect \\
Certified Information Systems Security Professional (CISSP)

\section{\mysidestyle Experience}
{\bf Sandia National Laboratories}, Albuquerque, New Mexico \vspace{2mm} \\
{\sl Principal Member of Technical Staff} \hfill \textbf{April 2008 -- Present} \\
{\sl Limited Term Employee} \hfill \textbf{October 2005 -- April 2009} \\
{\sl Contractor, RESPEC} \hfill \textbf{March 2004 -- October 2005} \\
Architecture development and security analysis; ICAM architectures; heterogeneous analytic component systems engineering; program development; micro-controller engineering (PIC32, PIC16); service-oriented system architecture, design, and development; software engineering; general project management 

{\bf Oso Grande Technologies}, Albuquerque, New Mexico \vspace{2mm} \\
{\sl Vice President, Software Engineering} \hfill \textbf{October 2003 -- March 2004} \\
{\sl Manager, Software Engineering} \hfill \textbf{March 2001 -- October 2004} \\
Led a multi-disciplinary team brokering information via web services between national insurance aggregators and state governments; responsible for profitability, business development, technical architecture and development

\section{\mysidestyle Selected Publications}
C.C. Lamb and G.L. Heileman.
\newblock Overlay architectures enabling cloud computing for multi-level
  security environments.
\newblock In {\em Services (SERVICES), 2012 IEEE Eighth World Congress on},
  pages 116 --124, june 2012.

Christopher~Charles Lamb, Pramod~A. Jamkhedkar, Mathew~P. Bohnsack, Viswanath
  Nandina, and Gregory~L. Heileman.
\newblock A domain specific language for usage management.
\newblock In {\em Proceedings of the 11th annual ACM workshop on Digital rights
  management}, DRM '11, pages 51--62, New York, NY, USA, 2011. ACM.

Christopher~C. Lamb, Pramod~A. Jamkhedkar, Gregory~L. Heileman, and Chaouki~T.
  Abdallah.
\newblock Managed control of composite cloud systems.
\newblock In {\em System of Systems Engineering (SoSE), 2011 6th International
  Conference on}, pages 167 --172, june 2011.

P.A. Jamkhedkar, C.C. Lamb, and G.L. Heileman.
\newblock Usage management in cloud computing.
\newblock In {\em Cloud Computing (CLOUD), 2011 IEEE International Conference
  on}, pages 525 --532, july 2011.

Pramod~A. Jamkhedkar, Gregory~L. Heileman, and Chris~C. Lamb.
\newblock An interoperable usage management framework.
\newblock In {\em Proceedings of the tenth annual ACM workshop on Digital
  rights management}, DRM '10, pages 73--88, New York, NY, USA, 2010. ACM.

\end{resume}
\end{document}