\documentclass[margin,line]{resume}

\begin{document}
\name{\Large Christopher C. Lamb}
\begin{resume}

\section{\mysidestyle Contact\\Information}
Christopher C. Lamb							\hfill home: 505.284.2379				\vspace{0mm}\\\vspace{0mm}%
7400 Yarwood St. NE							\hfill mobile: 505.228.8090 		\vspace{0mm}\\\vspace{0mm}%
Albuquerque, NM 87109						\hfill e-mail: cclamb@ece.unm.edu		  	\vspace{0mm}\\\vspace{-4.5mm}%

\section{\mysidestyle Education}

\textbf{Ph.D Computer Engineering} \\
\textsl{University of New Mexico} \hfill \textbf{ December 2012 } \\\vspace{-3mm}%
\begin{list2}
\item Concentration: Computational Intelligence
\item Advisor:  Professor Greg Heileman
\item Dissertation Topic: Information Protection in Content-centric Networks
\end{list2}
{\bf M.S. Computer Science}, University of New Mexico \\
{\bf B.S. Mechanical Engineering}, New Mexico State University

\section{\mysidestyle Certifications}
TOGAF 9 Certified Enterprise Architect \\
Certified Information Systems Security Professional (CISSP)

\section{\mysidestyle Clearances}
I currently hold a DOE Q Clearance.

\section{\mysidestyle Repositories}
{\bf github} \vspace{2mm}  \\
{\sl http://www.github.com/cclamb} \vspace{1mm} \\
An assortment of public and private repositories, demonstrating active and recent development efforts using Ruby, Python, Node.js, ASM/C/C++, and Erlang in embedded, distributed, and cloud environments.

\section{\mysidestyle Research Interests}
Dynamic Security Provisioning in Cloud Environments \\
Software Defined Networks and Infrastructure \\
Security in Cloud Robotics and Autonomous Systems

\section{\mysidestyle Experience}
{\bf Sandia National Laboratories}, Albuquerque, New Mexico \vspace{2mm} \\
{\sl Principal, Research \& Development, Computer Science} \hfill \textbf{April 2008 -- Present} \\
{\sl Limited Term Employee} \hfill \textbf{October 2005 -- April 2008} \\\vspace{1mm}%
{\sl Contractor, RESPEC} \hfill \textbf{March 2004 -- October 2005} \\
I most recently developed international-scale system architectures focused on protecting the federal enterprise, outlined strategies for emerging technologies (Cloud, Mobile), advised on specific malicious agent countermeasure strategies and system implementation, and prototyped large scale ($10^6$) event data analysis, visualization, and mining systems; was also engaged in micro-controller engineering (PIC32, PIC16), service-oriented system architecture, design, and development, general software engineering, and software project management.

{\bf The University of New Mexico}, Albuquerque, New Mexico \vspace{2mm} \\\vspace{1mm}%
{\sl Research Assistant Professor} \hfill \textbf{December 2012 -- Present} \\
Most recently focused on dynamic security provisioning within large scale cloud systems ranging from storage to network to consumption, ARM TrustZone and roots of trust, cloud robotic systems, and software-defined networking.  Also responsible for guiding graduate student research, helping with papers, and sitting on committees.

{\bf Oso Grande Technologies}, Albuquerque, New Mexico \vspace{2mm} \\
{\sl Vice President, Software Engineering} \hfill \textbf{October 2002 -- March 2004} \\\vspace{1mm}%
{\sl Manager, Software Engineering} \hfill \textbf{March 2001 -- October 2002} \\
At Oso Grande Technologies I led a multi-disciplinary team brokering information via web services between national insurance aggregators and state governments; was responsible for profitability, business development, and technical architecture and development.

\newpage

\section{\mysidestyle Languages and Frameworks}
Python (OpenStack, Pox) \\
Ruby (Sinatra, Rails) \\
HTML5/CSS/Javascript (D3, JQuery, extjs) \\
Javascript (Node.js) \\
Java (OSGi, JEE, Project Floodlight) \\
C/C++ (PIC/MPLAB, GNU/ARM, GNU/Linux) \\
Hadoop \\
Accumulo \\
OpenStack

\section{\mysidestyle Patents}
{\small System and Methods for Usage Management in Multi-Level Security Networks (2013)} \\
{\small System and Methods of Resource Usage using an Interoperable Management Framework (2012)} \\
{\small System and Methods for Usage Management of Personal Medical Records (2011)}

\section{\mysidestyle Selected Publications}
Viswanath Nandina, Jose~Marcio Luna, Edward~J. Nava, Christopher~C. Lamb,
  Gregory~L. Heileman, and Chaouki~T. Abdallah.
\newblock Policy-based security provisioning and performance control in the
  cloud.
\newblock In {\em Cloud Computing and Services Science, 2013 4th International
  Conference on}, May 2013.
  
Christopher Lamb and Gregory Heileman.
\newblock Content-centric information protection in cloud computing.
\newblock {\em International Journal of Cloud Computing and Services Science},
  2(1):246--257, 2012.

Christopher~C. Lamb, Pramod~A. Jamkhedkar, and Gregory~L. Heileman.
\newblock {\em Digital Rights Management: Technology, Standards and
  Applications}.
\newblock Auerbach Publications, 2013.

C.C. Lamb and G.L. Heileman.
\newblock Overlay architectures enabling cloud computing for multi-level
  security environments.
\newblock In {\em Services (SERVICES), 2012 IEEE Eighth World Congress on},
  pages 116 --124, june 2012.

%Christopher~Charles Lamb, Pramod~A. Jamkhedkar, Mathew~P. Bohnsack, Viswanath
%  Nandina, and Gregory~L. Heileman.
%\newblock A domain specific language for usage management.
%\newblock In {\em Proceedings of the 11th annual ACM workshop on Digital rights
%  management}, DRM '11, pages 51--62, New York, NY, USA, 2011. ACM.

%Christopher~C. Lamb, Pramod~A. Jamkhedkar, Gregory~L. Heileman, and Chaouki~T.
%  Abdallah.
%\newblock Managed control of composite cloud systems.
%\newblock In {\em System of Systems Engineering (SoSE), 2011 6th International
%  Conference on}, pages 167 --172, june 2011.

P.A. Jamkhedkar, C.C. Lamb, and G.L. Heileman.
\newblock Usage management in cloud computing.
\newblock In {\em Cloud Computing (CLOUD), 2011 IEEE International Conference
  on}, pages 525 --532, july 2011.

\end{resume}
\end{document}